---
title: "Romance With R"
author: "Sree"
date: "12/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown Book. 

> Commenting in R Language :

```{r}
# This is single line commenting
# Line 1
# Line 2
# Line 3
#<ctrl> <shift> <c> on mulliple lines comments the lines. 

```

There is no multi line or block commenting in R. Selecting multiple lines to comment and use \<ctrl>\<shift>\<c> to comment out them.

> Traditional Hello World :

```{r}
print("Hello World")
```

```{r}
 # paste  and paste0
paste("file" , "number", 32)

```

```{r}
paste("file", "Number", 32, sep = "-")
```

```{r}
paste0("File", "number", 32)

```

```{r}
# String concatenation
cat("Hello " , "World")
```

## Chapter 1 - Data Types

#### 1.1 Scalars & Vectors : 

One way to classify the data types is Scalars and Vectors . Scalars are atomic values like a single number, string , float value etc. Basically they store one unit atomic value. Where as vectors are basically collections of scalars.

If 'integer' is a scalar, an array of "integers" is vector. Please note Vectors always store same type elements in them.

*typeof(), class()* are two commands that show the details of a data element.

```{r echo=TRUE}
# Some Examples of data elements
a <- 20
print(typeof(a))
print(class(a))

```

```{r echo = TRUE}
name <- "sree"
singlechar <- 'c'
print(typeof(name))
print(class(name))
print(typeof(singlechar))
print(class(singlechar))

```

\
